---
title: "Lab 03 - Nobel laureates"
author: "Kryschelle Fakir"
date: "2/6/2026"
output: github_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

```{r load-data, message=FALSE}
nobel <- read_csv("data/nobel.csv")
```

## Exercises

Here is a link to the [lab instructions](https://datascience4psych.github.io/DataScience4Psych/lab03.html).

### Exercise 1

```{Data Frame with Still Alive, Country, and no Orgs}
# There are 1026 observations and 26 variables in the nobel dataset. Each row represents a nobel prize winner.

nobel %>%
  filter( 
    is.na(died_date),
    !is.na(country), 
    gender != "org"
  ) 
```

Remove this text, and add your answer for Exercise 1 here.
Add code chunks as needed.
Don't forget to label your code chunk.
Do not use spaces in code chunk labels.

### Exercise 2

Remove this text, and add your answer for Exercise 1 here.
Add code chunks as needed.
Don't forget to label your code chunk.
Do not use spaces in code chunk labels.

### Exercise 3

Remove this text, and add your answer for Exercise 1 here.
Add code chunks as needed.
Don't forget to label your code chunk.
Do not use spaces in code chunk labels.

### Exercise 4

...

### Exercise 5

...

### Exercise 6

...
