---
title: "Lab 03 - Nobel laureates"
author: "Kryschelle Fakir"
date: "2/6/2026"
output: github_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

```{r load-data, message=FALSE}
nobel <- read_csv("data/nobel.csv")
```

## Exercises

Here is a link to the [lab instructions](https://datascience4psych.github.io/DataScience4Psych/lab03.html).

### Exercise 1

```{r make-living-nobel-winners-data}

nobel_living <- nobel %>%
  filter( 
    is.na(died_date),
    !is.na(country), 
    gender != "org"
  ) 
```

There are 1026 observations and 26 variables in the nobel dataset. Each row represents a nobel prize winner.

### Exercise 2

```{r make-based-in-us}

nobel_living <- nobel_living %>%
  mutate(
    country_us = if_else(country == "USA", "USA", "Other")
  )

nobel_living_science <- nobel_living %>%
  filter(category %in% c("Physics", "Medicine", "Chemistry", "Economics"))

```

### Exercise 3

```{r make-barplot}

ggplot(
  data = nobel_living_science,
       mapping = aes(
         x = country_us
       )
) + 
  geom_bar() +
  facet_wrap(~category) + 
  coord_flip() + 
  labs(
    title = "Relationship B/T Category and Country",
    subtitle = "Country being whether the recipient was in the U.S when they won",
    x = "In the US or Not",
    y = "Category"
  )

```

Based on the visualization, it does seem that most winners were based in the US when they won their nobel prize. However, the Chemistry and Physics categories are very close, especially compared to the Economics category. This may suggest that lots of folks are studying the U.S' economics (I wonder why... >:T)

### Exercise 4
```{r make-born-in-us-variable}

nobel_living <- nobel_living %>%
  mutate(
    born_country_us = if_else(born_country == "USA", "USA", "Other")
  ) 

nobel_living %>%
  count(born_country_us)

```

113 of the U.S based Nobel laureates were born in the U.S. 

### Exercise 5

```{r make-born-in-us-barplot, warning=TRUE}

nobel_living_science <- nobel_living_science %>%
  mutate(
    born_country_us = if_else(born_country == "USA", "USA", "Other")
  ) 

ggplot(
  data = nobel_living_science,
       mapping = aes(
         x = country_us,
         fill = born_country_us
       )
) + 
  geom_bar() +
  facet_wrap(~category) + 
  coord_flip() + 
  labs(
    title = "Relationship B/T Category and U.S. Based",
    subtitle = "By U.S. Born",
    fill = "Born in the U.S",
    x = "U.S Based or Other",
    y = "Category"
  ) 

```

Based on the visualization above, Buzzfeed's claim is incorrect. Majority of the U.S based Nobel Laureates are born in the U.S. Of those based in the U.S, regardless of  category, majority are born in the U.S. 

### Exercise 6

...
